
\chapter{Conclusions}

    We have tried to proposed two different types of memory management frameworks, one is a 
    simple update to the existing memory management controller and the other is a decentralized
    memory management framework for derivative clouds.
    
    \section{Differentiated memory management controller}
  
    We have made an initial attempt to understand the working of memory management in Linux
    containers. We identified issues with the existing memory management controller used to
    provision containers in a native and derivative cloud environment. We have empirical 
    verified our hypotheses. 
    
    We then have proposed a differentiated memory management 
    controller by making modifications to the existing controller. Our controller supports
    different types of memory management policies among containers provisioned using a Linux
    containers framework. We have demonstrated the working of this controller and evaluated the 
    effectiveness of controller in overcoming the pitfalls of the existing controller. 
    Our controller has shown its ability of differentiated memory provisioning among containers 
    and how it positively impacts application performance.
    
    \section{Decentralized memory management framework}
  
    We made an attempt in understanding hypervisor caching frameworks and how they are used to 
    meet application level objectives. We then proposed modifications to existing cache partitioning
    frameworks to support derivative clouds, however such a framework still failed to help anonymous 
    memory sensitive applications and other complicated cache partitioning constraints. 
    
    We then proposed a decentralized memory management framework where the hypervisor is only responsible 
    for partitioning the caches at the VM level and the controller inside the guest is responsible allocating the 
    - container memory and other levels of caches at the hypervisor to meet application specific needs. Our new design 
    also incorporates an hybrid cache design where cache partitioning at the hypervisor can incorporate a 
    two level hybrid partition. We demonstrated the effectiveness of our new controller by provisioning for
    applications of all kinds and showed how our memory management framework triumphs over other traditional 
    cache partitioning frameworks in meeting application objectives. We also demonstrated the effectiveness of
    our hybrid implementation by provisioning an application at two levels simultaneously. 
    
    Our former contribution on a differentiated memory management controller has been accepted at 
    \textit{IEEE ICDCS '17 (International Conference on Distributed Computing Systems 2017)} in the poster track, 
    and the latter contribution on \dd{}---Decentralized management framework for derivative clouds is in
    submission at \textit{ACM Middleware '17}.
    
    